The dependence of spiral disk morphology on the star formation-stellar mass relation

### 2014-09-11 paper/mainsequence_morph.tex
Added potential co-author list, 1st round of comments

\author{Kyle Willett\altaffilmark{1}, Kevin Schawinski\altaffilmark{2}, etc.}

@@

@@

In this paper, we use the Sloan Digital Sky Survey \citep{yor00,str02,aba09} in combination with the largest database of visual classifications of galaxy structure and morphology ever assembled from the Galaxy Zoo citizen science projects \citep{lin08,lin11,wil13} to test whether galaxy structure affects their star formation properties.

@@

Stellar masses and star formation rates are computed from optical diagnostics and taken from the MPA-JHU catalogue \citep{kau03a,bri04}. We use updated masses and activity classifications from the DR7 database.\footnote{\url{http://home.strw.leidenuniv.nl/\mytilde jarle/SDSS/}} We separate star-forming galaxies from other emission-line galaxies using the standard BPT classification \citep{bal81} below the \citet{kau03} demarcation. Galaxies with low signal-to-noise ratio $(S/N > 3)$ galaxies are removed. For both $M_\star$ and $SFR$, we use median values extracted from the PDF.

@@

As a comparison to the kpc-scale structures discussed above, we analyze the impact of the most significant forcing event to a galaxy system known -- a major galaxy merger (Figure~\ref{fig-mergers}). In these systems (which are in various stages of coalescence) the star formation rates are increased by only an average of 0.29~dex, corresponding to less than a factor of two overall. \citet{dar10} showed that in the local ($z<0.1$) Universe, galaxies with intense bursts of star formation are limited to only the spiral (disc) galaxies. This increase in star formation for mergers does show a strong evolution in redshift out to at least $1.5<z<2.5$, likely due to the higher gas fractions involved \citep{dad10,rod11}.

@@

We thank Rory Smith and Lucio Mayer for useful discussions. This research made use of TOPCAT, an interactive graphical viewer and editor for tabular data \citep{tay05}. 
%The development of Galaxy Zoo 2 was supported by The Leverhulme Trust. KWW and LFF would like to acknowledge support from the US National Science Foundation under grant DRL-0941610. CJL acknowledges support from the Science and Technology Facilities Council (STFC) Science in Society program. KS gratefully acknowledges support from Swiss National Science Foundation Grant PP00P2\_138979/1. TM acknowledges funding from the STFC ST/J500665/1. RCN was partially supported by STFC grant ST/K00090X/1. BDS acknowledges support from Worcester College, Oxford, and from the Oxford Martin School program on computational cosmology.

>>>>

\author{Kyle Willett\altaffilmark{1}, Kevin Schawinski\altaffilmark{2}, etc.}
% People who want to be co-authors:
% Ivy Wong
% Karen Masters
% Ramin Skibba
% Bob Nichol
% Tom Melvin
% Edmond Cheung
% Chris Lintott
% Bill Keel
% Sugata Kaviraj

@@

%@arxiver{ms_bar_contour.pdf,ms_mergers_both.pdf}

@@

In this paper, we use the Sloan Digital Sky Survey \citep{yor00,str02,aba09} in combination with the largest database of visual classifications of galaxy structure and morphology ever assembled from the Galaxy Zoo citizen science projects \citep{lin08,lin11,wil13} to test whether galaxy structure affects their star formation properties. We use the WMAP9 cosmology parameters of $(\Omega_m,\Omega_\Lambda,h)=(0.258,0.718,0.697)$ \citep{hin13}.

@@

Stellar masses and star formation rates are computed from optical diagnostics and taken from the MPA-JHU catalogue \citep{kau03a,bri04,sal07}. We use updated masses and activity classifications from the DR7 database.\footnote{\url{http://home.strw.leidenuniv.nl/\mytilde jarle/SDSS/}} We separate star-forming galaxies from other emission-line galaxies using the standard BPT classification \citep{bal81} below the \citet{kau03} demarcation. Galaxies with low signal-to-noise ratio $(S/N > 3)$ galaxies are removed. For both $M_\star$ and $SFR$, we use median values extracted from the PDF.

@@

As a comparison to the kpc-scale structures discussed above, we analyze the impact of the most significant forcing event to a galaxy system known -- a major galaxy merger (Figure~\ref{fig-mergers}). In these systems (which are in various stages of coalescence) the star formation rates are increased by only an average of 0.29~dex, corresponding to less than a factor of two overall. \citet{dar10} showed that in the local ($z<0.1$) Universe, galaxies with intense bursts of star formation are limited to only the spiral (disc) galaxies. This increase in star formation for mergers does show a strong evolution in redshift out to at least $1.5<z<2.5$, likely due to the higher gas fractions involved \citep{dad10,rod11}. The projected separation between galaxies in which this occurs, based on both the observed merger fraction and sSFR is $\sim0.1$~Mpc$/h$ \citep{ski09}.

@@

We thank Rory Smith and Lucio Mayer for useful discussions. This research made use of TOPCAT, an interactive graphical viewer and editor for tabular data \citep{tay05} and Astropy, a community-developed core Python package for astronomy \citep{ast13}. 
%The development of Galaxy Zoo 2 was supported by The Leverhulme Trust. KWW and LFF would like to acknowledge support from the US National Science Foundation under grant DRL-0941610. CJL acknowledges support from the Science and Technology Facilities Council (STFC) Science in Society program. KS gratefully acknowledges support from Swiss National Science Foundation Grant PP00P2\_138979/1. TM acknowledges funding from the STFC ST/J500665/1. RCN was partially supported by STFC grant ST/K00090X/1. BDS acknowledges support from Worcester College, Oxford, and from the Oxford Martin School program on computational cosmology.
